Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-23 awipev-CO2.Rmd
variable names updates

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
                               ifelse (pressure_insitu_ctd >=8 ,temp_insitu_ctd, NA )))
```

@@

            dySeries("sal_fb", color = "blue", strokeWidth = 1, label = "sal_fb") %>%

@@

# pH seaFET Final
# add spectro points that are not taking into consideration
d_all <- d_all%>%
  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", ph_s_sf_temp_mix, NA ))

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT, ph_s_sf_temp_mix, pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd, sal_insitu_ctd, temp_insitu_ctd)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
dySeries("temp_insitu_ctd", axis="y",label = "T ctd", color ="grey", strokeWidth=0, pointSize=2) %>%
dySeries("sal_insitu_ctd", axis="y",label = "S ctd", color ="orange", strokeWidth=0, pointSize=2) %>%
dySeries("pressure_insitu_ctd", axis="y2",label = "Pression", color ="pink", strokeWidth=0, pointSize=2) %>%
dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%

  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%

  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
  #  dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
  #  dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
  #  dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
  #  dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
  #  dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

seafet_depth_xts <- dplyr::select(d_all, datetime, phINT, ph_s_sf_temp_mix,pHint_tot_sf)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
  dySeries("ph_s_sf_temp_mix", axis="y2", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dySeries("phINT", axis="y2",label = "pH RAW", color ="blue", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
  dySeries("pHint_tot_sf", axis="y2", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

>>>>

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
                               ifelse (pressure_insitu_ctd >=8 ,temp_insitu_ctd, NA )))

# qf added 
d_all <- d_all %>% 
  dplyr::mutate(
    temp_fb_qf = ifelse(
      State_Zero >= 1 | State_Flush >= 1 |
        pco2_raw < 100 | pco2_raw > 450 |
        Time >= "00:00:00" & Time <= "01:30:00" |
        Time >= "12:00:00" & Time <= "13:00:00" |
        datetime == "2017-03-22 08:00:00" ,
      4,
      1
    ),
    pco2_raw = ifelse(pco2_raw_qf == 4 , NA, pco2_raw),
    pco2_corr_qf = ifelse(
      State_Zero >= 1 | State_Flush >= 1 |
        pco2_corr < 100 | pco2_corr > 450 |
        Time >= "00:00:00" & Time <= "01:30:00" |
        Time >= "12:00:00" & Time <= "13:00:00" |
        datetime >= "2017-03-10 08:00:00" &
        datetime < "2017-03-21 20:00:00",
      4,
      1
    ),
    pco2_corr = ifelse(pco2_corr_qf == 4 , NA, pco2_corr)
  )
```

@@

            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%

@@

# pH seaFET Final
# add despike with n=2 k = 5762 to the final ph corrected data
d_all <- d_all %>%     
   dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA"))

# add spectro points that are not taking into consideration
d_all <- d_all%>%
  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 10:00:00" | datetime == "2019-01-18 11:00:00", ph_s_sf_temp_mix, NA ))

@@

seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix,pHint_tot_sf, pHint_tot_sf_filtered, pH_s_sf_no_calb)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
dySeries("pHint_tot_sf_filtered", label = "pHint_tot_sf_filtered", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 2) %>%
dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%

  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyAxis("y2",valueRange = c(-2, 2)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
